Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-07-17 manuscript/manuscript.tex
Started writing implementation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}

>>>>

\section{Implementation}

We have developed a Python library that computes the gravity fields generated by any Tesseroid with variable density in depth that is freely available under the BSD 3-clause open-source library and can be downloaded from the following repository: \todo{agregar repo, vale la pena poner el link?}

Although it's a Python library, the core functions of the computation are written in Cython, a superset of Python language that allows us generate efficient C code through the Cython compiler.
This produces a precompiled library whose functions and classes can be called from regular Python code, what allowed us to make it compatible with the preexisting open-source library Fatiando a Terra \citep{Uieda2013}.

Its usage is very similar to the code for homogeneous tesseroid already in Fatiando a Terra (version 0.5):

\begin{enumerate}
\renewcommand{\theenumi}{(\arabic{enumi})}
\item Define a single tesseroid (or a tesseroid mesh) with the Fatiando a Terra classes.
\item Add a predefined Python density function to the tesseroid (or each tesseroid in the mesh).
\item Calculate the desired gravity field (potential, gradient or tensor component) in any set of computation points with our new functions.
\end{enumerate}

The existing code in Fatiando a Terra (v.~0.5) for homogeneous tesseroid is optimised through the Numba compiler.
Due to difficulties when passing a Python function as argument of precompiled Numba methods, we have decided to rewrite them in Cython language, keeping the homogeneous tesseroid calculation and adding the new variable density code.

\todo{speed comparission between homogeneous and variable density}

\section{Acknowledgments}
